Title

### 2019-05-22 4_method.tex
show new instability issue

This needs to be stable against small perturbations in the outline polygon.
See \cref{heterogeneous_joint_generation}.
For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
Based on the MAT distance there we place ticks along the non-marked bones.

\begin{figure}[H]
\includegraphics[width=\columnwidth]{sources/method/heterogeneous_joint_generation.pdf}
\caption{Toolpaths employing dist rounding vs without.}
\label{heterogeneous_joint_generation}
\end{figure}

@@

In the following we assume an even spacing, i.e. $\win = \wout$.

One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
However, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
\hl{Does that mean the angle of the bones should ideally be updated?}

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/angular_based_spacing.pdf}
\caption{Angular based spacing isn't feasible. The bottom medial axis bone has different spacing based on the two patches. The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
\label{angular_based_spacing}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
\end{subfigure}
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
\label{medial_axis_parabolas_functions}
\end{subfigure}
\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline. Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
\label{medial_axis_parabolas}
\end{figure}

>>>>

This needs to be stable against small perturbations in the outline polygon.
See \cref{heterogeneous_joint_generation}.
For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
Based on the MAT distance $R$ there we place ticks along the non-marked bones following the beading strategy.

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/heterogeneous_joint_generation.pdf}
\caption{Toolpaths employing dist rounding vs without.}
\label{heterogeneous_joint_generation}
\end{figure}

@@

(In this subsection we assume an even spacing beading strategy, i.e. $\win = \wout$.)

A related problem is that that applying the beading strategy to highly skewed quads would not be stable to the addition of extra bones.
See \cref{quad_instability}.
\hl{We should introduce bones in such a case!}

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/quad_instability.pdf}
\caption{The addition of the extra bone (orange) causes a significant change from the dark red path to the green path.}
\label{quad_instability}
\end{figure}

See \cref{angular_based_spacing}.
One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
However, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
\hl{Does that mean the angle of the bones should ideally be updated?}

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/angular_based_spacing.pdf}
\caption{Angular based spacing isn't feasible. The bottom medial axis bone has different spacing based on the two patches. The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
\label{angular_based_spacing}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
\end{subfigure}
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
\label{medial_axis_parabolas_functions}
\end{subfigure}
\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline. Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
\label{medial_axis_parabolas}
\end{figure}
